WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-14 ms.tex
Some of Chris' comments

When (as in our assumptions) the likelihood is Gaussian, Equation~(\ref{eq:general-fisher-matrix}) simplifies to
%
\begin{equation}\label{eq:gaussian-fisher-matrix}
    \mathcal{I}_{jk} = \int_0^\infty \Re \left[
        \left(\frac{\partial X_i}{\partial \theta_j}\right)^*
        \left(\frac{\partial X_i}{\partial \theta_k}\right)
    \right] \frac{1}{S_i(\omega)} \, d\omega.
\end{equation}
%
This form is useful because it involves manipulating the signal $X_i (\omega)$ rather than the entire observation $Y (\omega)$. In terms of the $k$th \ac{SNR}-weighted moment of angular frequency,
%
\begin{equation}\label{eq:angular-frequency-moments}
    {\overline{\omega^k}}_i =
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \omega^k \, d\omega \right]
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \, d\omega \right]^{-1},
\end{equation}
%
the Fisher matrix for the signal in the $i$th detector is
%
\begin{equation}
    \label{eq:single-detector-block-fisher-matrix}
    \mathcal{I}_i = \left(
        \begin{array}{cc}
            \mathcal{I}_{\bm\theta_i,\bm\theta_i} &
            \mathcal{I}_{\bm\theta_i,\bm\theta_\mathrm{in}} \\
            {\mathcal{I}_{\bm\theta_i,\bm\theta_\mathrm{in}}}\transpose &
            {\rho_i}^2 \mathcal{I}_{\bm\theta_\mathrm{in},\bm\theta_\mathrm{in}}
        \end{array}
    \right).
\end{equation}
%
The top-left block describes only the extrinsic parameters, and is given by
%
\begin{equation}\label{eq:fisher-matrix}
    \mathcal{I}_{\bm\theta_i,\bm\theta_i} = \bordermatrix{
        ~ & \rho_i & \gamma_i & \tau_i \cr
        \rho_i & 1 & 0 & 0 \cr
        \gamma_i & 0 & {\rho_i}^2 & -{\rho_i}^2 {\overline{\omega}}_i \cr
        \tau_i & 0 & -{\rho_i}^2 {\overline{\omega}}_i & {\rho_i}^2 {\overline{\omega^2}}_i
    }.
\end{equation}
%
(This is equivalent to an expression given in \cite{Grover:2013}.) The bottom row and right column of Equation~(\ref{eq:single-detector-block-fisher-matrix}) describe the intrinsic parameters and how they are coupled to the extrinsic parameters. We show in Appendix~\ref{sec:independence-intrinsic-extrinsic} that we need not consider the intrinsic parameters at all if we are concerned only with sky localization.

>>>>

When (as in our assumptions) the likelihood is Gaussian,\footnote{This assumes that the merger occurs at a frequency outside the sensitive ``bucket'' of the detector's noise \ac{PSD}. There are additional terms if the \ac{GW} spectrum drops to zero within the sensitive bandwidth of the detector, as can be the case for \ac{NSBH} mergers; see \cite{2014CQGra..31o5005M}.} Equation~(\ref{eq:general-fisher-matrix}) simplifies to
%
\begin{equation}\label{eq:gaussian-fisher-matrix}
    \mathcal{I}_{jk} = \int_0^\infty \Re \left[
        \left(\frac{\partial X_i}{\partial \theta_j}\right)^*
        \left(\frac{\partial X_i}{\partial \theta_k}\right)
    \right] \frac{1}{S_i(\omega)} \, d\omega.
\end{equation}
%
This form is useful because it involves manipulating the signal $X_i (\omega)$ rather than the entire observation $Y (\omega)$. In terms of the $k$th \ac{SNR}-weighted moment of angular frequency,
%
\begin{equation}\label{eq:angular-frequency-moments}
    {\overline{\omega^k}}_i =
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \omega^k \, d\omega \right]
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \, d\omega \right]^{-1},
\end{equation}
%
the Fisher matrix for the signal in the $i$th detector is
%
\begin{equation}
    \label{eq:single-detector-block-fisher-matrix}
    \mathcal{I}_i = \left(
        \begin{array}{cc}
            \mathcal{I}_{\bm\theta_i,\bm\theta_i} &
            \mathcal{I}_{\bm\theta_i,\bm\theta_\mathrm{in}} \\
            {\mathcal{I}_{\bm\theta_i,\bm\theta_\mathrm{in}}}\transpose &
            {\rho_i}^2 \mathcal{I}_{\bm\theta_\mathrm{in},\bm\theta_\mathrm{in}}
        \end{array}
    \right).
\end{equation}
%
The top-left block describes only the extrinsic parameters, and is given by
%
\begin{equation}\label{eq:fisher-matrix}
    \mathcal{I}_{\bm\theta_i,\bm\theta_i} = \bordermatrix{
        ~ & \rho_i & \gamma_i & \tau_i \cr
        \rho_i & 1 & 0 & 0 \cr
        \gamma_i & 0 & {\rho_i}^2 & -{\rho_i}^2 {\overline{\omega}}_i \cr
        \tau_i & 0 & -{\rho_i}^2 {\overline{\omega}}_i & {\rho_i}^2 {\overline{\omega^2}}_i
    }.
\end{equation}
%
(This is equivalent to an expression given in \cite{Grover:2013}.) The bottom row and right column of Equation~(\ref{eq:single-detector-block-fisher-matrix}) describe the intrinsic parameters and how they are coupled to the extrinsic parameters. We show in Appendix~\ref{sec:independence-intrinsic-extrinsic} that we need not consider the intrinsic parameters at all if we are concerned only with sky localization.
